DOpElib:\\ Differential Equations and Optimization Environment

### 2019-03-20 Examples/PDE/InstatPDE/Example9/content.tex
Added inhomogeneous Dirichlet-data to Example/InstatPDE/Example9 to show Bug with hanging nodes on inhomogeneous Dirichlet Boundaries

In this example we consider one of the prototypical nonstationary equations, the parabolic heat equation, i.e. for $x \in \Omega \subset \mathbb{R}^d, t\in I =[0,T], T\in \mathbb{R}^+,$ we search for the unknown solution $u:I \times \Omega \rightarrow \mathbb{R}$
\begin{align*}
\partial_t u(t,x) - \Delta u(t,x) &= f(t,x),\\
u(t,x)|_{\partial \Omega} &= g(t,x),\\
u(0,x) &= u_0(x).
\end{align*} In our example, we consider the simplest case $d=1$, where the Laplacian $\Delta$ reduces to $\partial_x^2$. The computational domain is $ I\times \Omega = [0,1] \times [0,1]^2$. For further simplification, we choose the right hand side as $f=0$ as well as homogeneous Dirichlet boundary conditions ($g=0$). The initial condition is given by $u_0(x) = \min(x_1,1-x_1)$.

>>>>

In this example we consider one of the prototypical nonstationary equations, the parabolic heat equation, i.e. for $x \in \Omega \subset \mathbb{R}^d, t\in I =[0,T], T\in \mathbb{R}^+,$ we search for the unknown solution $u:I \times \Omega \rightarrow \mathbb{R}$
\begin{align*}
\partial_t u(t,x) - \Delta u(t,x) &= f(t,x),\\
u(t,x)|_{\partial \Omega} &= g(t,x),\\
u(0,x) &= u_0(x).
\end{align*} In our example, we consider the simplest case $d=1$,
where the Laplacian $\Delta$ reduces to $\partial_x^2$. The
computational domain is $ I\times \Omega = [0,1] \times [0,1]^2$. For
further simplification, we choose the right hand side as $f=0$ and the
initial condition is given by $u_0(x) = \min(x_1,1-x_1)$.
The Dirichlet-data are
\[
  g(t,x) = \begin{cases} tx_2 & x_1 = 1,\\
    0 & \text{otherwise.}
  \end{cases}
\]
